\documentclass[conference]{IEEEtran}

\input{macros}
\input{config}

\pdfColorScheme{\myPdfColorScheme} % "0" is standard and should be used for submission and printing
\includeAuthorComments{\myIncludeAuthorComments} % "0" turns them off, otherwise they are on. Use \jim{} or \vijay{} or \jy{}

\begin{document}

% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{Not yet Decided}

\author{
\IEEEauthorblockN{Jungyoun Ku, Vijay Krishna Palepu, and James A. Jones}
\IEEEauthorblockA{University of California, Irvine, USA\\
\{jungyok, vpalepu, jajones\}@uci.edu}
}

\maketitle


\begin{abstract}
The abstract goes here.\\
\end{abstract}



\section{Introduction}

NOTE: this paper needs to be written while assuming a double-blind review. \emph{So we cannot refer to any of our prior work in the first-person -- it would have to be done in third person}. As such, the paper can only have sentences as follows. Jones and colleagues~\cite{palepu13sep,palepu2015revealing,deng11sep} in their work on visualizing runtime relationships between source code line \ldots

Sentences like the following \emph{may} result in a rejection. In our prior work on visualizing runtime relationships between source code lines~\cite{palepu13sep,palepu2015revealing,deng11sep} \ldots

Setting up comment colors:\\ 
\jim{This is how Jim's comments look}\\
\vijay{This is how Vijay's comments look}\\
\jy{This is how JY's comments look}\\

Golden formula for introductions (thanks to Jim Clause):
\begin{enumerate}
\item What's the problem?
\item Why is it important?
\item What is existing work
\item Why is existing work insufficient?
\item What are you doing?
\item How does that address the insuffiencies of existing work?
\item Contributions (ideally, should \textbf{start} on the second page --- no later)
\end{enumerate}





% You must have at least 2 lines in the paragraph with the drop letter
% (should never be an issue)

%\subsection{Subsection Heading Here}
%Subsection text here.

%\subsubsection{Subsubsection Heading Here}
%Subsubsection text here.

\section{Motivation}
The motivation goes here.

\section{Approach}
The approach goes here.

\section{Related Works}
The related works goes here.

\section{Evaluation}
The evaluation goes here.

\section{Conclusion}
The conclusion goes here.

\section*{Acknowledgment}
The authors would like to thank... NSF.
\\

\bibliographystyle{abbrv}
\bibliography{paper}

\end{document}